% Filename: kickoff_minutes.tex
\documentclass[a4paper,12pt]{article}
\usepackage[margin=1in]{geometry} 
\usepackage{parskip}               % blank lines instead of indent
\usepackage{hyperref}              % clickable links
\usepackage{graphicx}              % include images if needed
\usepackage{enumitem}              % control list spacing
\usepackage{fancyhdr}              % headers & footers
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% Header/footer setup
\pagestyle{fancy}
\fancyhf{}
\lhead{Kickoff Meeting Minutes}
\rhead{PSM Protech Feasibility Study}
\cfoot{\thepage}

\title{\Large\bfseries Kickoff Meeting Minutes\\[0.5ex]
       \normalfont PSM Protech Feasibility Analysis Project}
\author{Students Team \& PSM Protech GmbH}
\date{31 March 2025}

\begin{document}
\maketitle

\section*{1. General Information}
\begin{description}[leftmargin=!,labelwidth=\widthof{\bfseries Duration:}]
  \item[Date \& Time:] 31 March 2025, 10:00\,--\,12:00
  \item[Location:] PSM Protech GmbH headquarters
  \item[Duration:] Approximately 2 hours
\end{description}

\subsection*{Participants}
\begin{itemize}[noitemsep]
  \item Five student representatives (Engineering Master’s, TH Rosenheim)
  \item Prof.\ Dr.\ Michael Wagner (Project Supervisor)
  \item PSM Protech GmbH team
\end{itemize}

\subsection*{Distribution List}
\begin{itemize}[noitemsep]
  \item Project manager (PSM Protech GmbH)
  \item Department heads (Tribology \& AI teams)
  \item All students on the project team
  \item Prof.\ Dr.\ Wagner
\end{itemize}

\section*{2. Key Discussion Points}
\begin{enumerate}[label=\arabic*.,leftmargin=*]
  \item \textbf{Project Overview:} 
    \begin{itemize}[noitemsep]
      \item PSM Protech presented the overall goals: automate GD\&T extraction and tolerance feasibility analysis from mechanical drawings.
      \item Reviewed scope, timeline, and high-level deliverables.
    \end{itemize}
  \item \textbf{Dataset Preview:}
    \begin{itemize}[noitemsep]
      \item Company provided sample PDF drawings and CSV reports.
      \item Discussed data formats (SVG/PDF for drawings, CSV for annotations).
    \end{itemize}
  \item \textbf{Project Aim \& Process Tour:}
    \begin{itemize}[noitemsep]
      \item Walked through PSM Protech’s engineering facilities.
      \item Highlighted manufacturing constraints and real-world tolerance checks.
    \end{itemize}
  \item \textbf{Next Steps:}
    \begin{itemize}[noitemsep]
      \item Await delivery of full dataset from PSM Protech.
      \item Student team to begin exploratory data analysis (EDA) and pipeline prototyping.
    \end{itemize}
\end{enumerate}

\section*{3. Decisions \& Action Items}
At this kickoff no individual task assignments were finalized. The student team will self-organize after dataset delivery. 

\begin{description}[leftmargin=!,labelwidth=\widthof{\bfseries Tasks to Date:}]
  \item[Tasks:] 
    \begin{itemize}[noitemsep]
      \item \emph{Pending Dataset}: PSM Protech to supply the remainder of drawing files and CSV annotations.
      \item \emph{Exploratory Analysis}: Students to prepare initial report on data quality and required preprocessing steps.
    \end{itemize}
  \item[Responsible:] Student team (collectively)
  \item[Due:] TBD (upon dataset arrival)
  \item[Binding Notes:] None at this stage
\end{description}

\section*{4. Repository \& Archiving}
\begin{itemize}[noitemsep]
  \item Invitation and this minutes document stored under \texttt{Documentation/} folder in project repository.
  \item Meeting agenda, slides, and photos of whiteboard sketches are likewise committed.
  \item Wiki page (\url{https://gitlab.example.com/yourproject/wiki/Kickoff}) links to all materials.
\end{itemize}

\vfill
\hrulefill\\
\small
\textit{Prepared by: Student Coordination Team}\\
\textit{Reviewed by: Prof.\ Dr.\ Michael Wagner, PSM Protech GmbH}

\end{document}