\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage{geometry}
\geometry{margin=1in}

\title{Project Milestones and Timeline}
\author{Team Wunderbar}
\date{\today}

\begin{document}

\maketitle

\section*{Weekly Project Timeline and Milestones}

\begin{longtable}{|p{2.5cm}|p{4.2cm}|p{8.5cm}|}
\hline
\textbf{Week} & \textbf{Dates (Mon–Sun)} & \textbf{Milestones and Tasks} \\
\hline
Week 1 & April 7 -- April 13, 2025 &
\begin{itemize}
    \item Set up the project repository.
    \item Define folder structure and annotation format.
    \item Finalize task board and management workflow.
    \item Conduct kickoff meeting to align goals and responsibilities.
\end{itemize} \\
\hline
Week 2 & April 14 -- April 20, 2025 &
\begin{itemize}
    \item Begin Phase 1 annotation on original images for Model 1.
    \item Set up the initial YOLO model environment and configurations.
\end{itemize} \\
\hline
Week 3 & April 21 -- April 27, 2025 &
\begin{itemize}
    \item Continue Phase 1 annotation.
    \item Begin training Model 1 (YOLO) using partially annotated data.
\end{itemize} \\
\hline
Week 4 & April 28 -- May 4, 2025 &
\begin{itemize}
    \item Finalize Phase 1 annotation.
    \item Complete training of YOLO (Model 1).
    \item Export bounding boxes and generate cropped outputs.
\end{itemize} \\
\hline
Week 5 & May 5 -- May 11, 2025 &
\begin{itemize}
    \item Start Phase 2 annotation using cropped images.
    \item Begin development of Model 2 (OCR + classification).
\end{itemize} \\
\hline
Week 6 & May 12 -- May 18, 2025 &
\begin{itemize}
    \item Continue Phase 2 annotation.
    \item Begin training Model 2 using labeled OCR data.
\end{itemize} \\
\hline
Week 7 & May 19 -- May 25, 2025 &
\begin{itemize}
    \item Continue Model 2 training and tuning.
    \item Start development of Model 3 (rule-based logic and formula calculations).
\end{itemize} \\
\hline
Week 8 & May 26 -- June 1, 2025 &
\begin{itemize}
    \item Finalize Model 3 logic and perform rule validation.
    \item Integrate Excel/CSV export pipeline.
\end{itemize} \\
\hline
Week 9 & June 2 -- June 8, 2025 &
\begin{itemize}
    \item Integrate Model 1, Model 2, and Model 3 into a unified pipeline.
    \item Conduct end-to-end testing and debugging.
\end{itemize} \\
\hline
Week 10 & June 9 -- June 15, 2025 &
\begin{itemize}
    \item Perform final QA and validation.
    \item Prepare project presentation and documentation.
    \item Submit the complete project deliverables.
\end{itemize} \\
\hline
\end{longtable}

\section*{Annotation Process Details}

\subsection*{Phase 1: Annotation for Model 1}
\begin{itemize}
    \item Annotate 300--400 original images with bounding boxes.
    \item These annotations are used to train Model 1 (YOLO) for object detection.
    \item The bounding box outputs are later used to crop regions of interest for further processing.
\end{itemize}

\subsection*{Phase 2: Annotation for Model 2}
\begin{itemize}
    \item Annotate cropped images generated from Model 1’s output.
    \item Focus on labeling text elements, symbols, and structured fields.
    \item Assign classification tags (e.g., ID, label, value) to the annotated components.
\end{itemize}

\subsection*{Phase 3: Rule-Based Processing (Model 3)}
\begin{itemize}
    \item Pass the classified outputs from Model 2 into a rule-based engine.
    \item Apply logical formulas to perform computations, content validation, or formatting.
    \item Export the final structured results to Excel or CSV files.
\end{itemize}

\end{document}