\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

\begin{document}

\section*{Project Constraints – Feasibility Analysis of Blueprints}

\begin{enumerate}
    \item \textbf{Input Quality Constraints}
    \begin{itemize}
        \item Blueprint variability in layout, resolution, or format.
        \item Presence of noise, smudges, or low contrast in scanned documents.
        \item Non-standard formats or annotations such as handwritten notes.
    \end{itemize}

    \item \textbf{Model Limitations}
    \begin{itemize}
        \item YOLO may struggle with ambiguous edges or overlapping regions.
        \item OCR accuracy may drop for technical fonts or skewed/noisy images.
    \end{itemize}

    \item \textbf{Feasibility Rule Complexity}
    \begin{itemize}
        \item Difficulty translating informal manufacturing rules into clear logic.
        \item Rules may evolve due to new technologies or changing tolerances.
    \end{itemize}

    \item \textbf{Annotation and Training Constraints}
    \begin{itemize}
        \item Annotating training data for rectangles and text is time-consuming.
        \item Access to blueprints may be limited due to confidentiality concerns.
    \end{itemize}

    \item \textbf{Tooling and Technical Constraints}
    \begin{itemize}
        \item High computational demand for training and inference.
        \item Need for compatibility with existing systems and file formats.
    \end{itemize}

    \item \textbf{User Constraints}
    \begin{itemize}
        \item Certain decisions may still require manual verification.
        \item Users expect clear and interpretable results from the system.
    \end{itemize}

    \item \textbf{Time and Resource Constraints}
    \begin{itemize}
        \item Limited project timeline to build and evaluate the system.
        \item Small team size or limited manpower may restrict model development.
    \end{itemize}

    \item \textbf{Evaluation Constraints}
    \begin{itemize}
        \item Ambiguity in defining correct outputs in complex or unclear cases.
        \item Defining and achieving realistic performance benchmarks.
    \end{itemize}
\end{enumerate}

\end{document}
